Data Preparation, Integration and Cleaning

### 2017-03-10 abbDataPrep_Script.Rmd
Fixed bookings bug

 # Remove existing 
 cut.fields <- which(names(str.data) %in% c('total.days', 'block.rate', 'avail.rate',
                                     'longest.block', 'nbr.block', 'med.block'))
 str.data <- str.data[ ,-cut.fields]

>>>>

 # Remove existing 
 cut.fields <- which(names(str.data) %in% c('total.days', 'block.rate', 'avail.rate',
                                     'longest.block', 'nbr.block', 'med.block', 'bookings'))
 str.data <- str.data[ ,-cut.fields]
